News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-11-17 rupnik2015.tex
cleaned up the bibliography

To test if the accuracy of the predictions is language dependent we have also performed the evaluations separately on individual language pairs. For this experiment we have split the annotated learning examples into three datasets, where each dataset contained only examples for one language pair. When training the classifier all three groups of features were available. The results are shown in Table~\ref{table:langPairEval}. We can see that the highest accuracy can be obtained when we need to decide if an English and German cluster represent the same event. A possible interpretation for these results is that this language pair has the most language resources (the highest number of Wikipedia pages) which results in the most accurate cross-lingual article similarity measure as well as the most extensive semantic annotation of the articles.

>>>>

To test if the accuracy of the predictions is language dependent we have also performed the evaluations separately on individual language pairs. For this experiment we have split the annotated learning examples into three datasets, where each dataset contained only examples for one language pair. When training the classifier all three groups of features were available. The results are shown in Table~\ref{table:langPairEval}. We can see that the performance of cluster linking on the English-German dataset is the highest in terms of accuracy, precision, recall and $F_1$. The performance on the English-Spanish dataset is comparable to the performance on the English-German dataset, where the former achieves higher recall (and slightly higher $F_1$ score), while the latter achieves higher precision. A possible explanation of these results is that the higher quantity and quality of English-German language resources leads to a more accurate cross-lingual article similarity measure as well as to a more extensive semantic annotation of the articles.
